---
title: "Summary Statistics"
author: "Widad Abdalla"
date: "2026-08-28"
output: html_document
---



1. load tidyverse package.

```{r q1, message=FALSE, warning=FALSE}



```

2. Read in the dataset `heart_study`.

```{r q2, message=FALSE, warning=FALSE}



```


3. For the variables: 
    systolic blood pressure,
    cigarettes per day, 
    body mass index, 
    heart rate, and
    glucose level
    Compute the following summary statistics 
    by Gender:
    1. Count the number of subjects
    2. Mean
    3. Standard Deviation
    4. Minimum
    5. Median 
    6. Maximum

```{r q3, message=FALSE, warning=FALSE}




```


4. For the variables: 
    systolic blood pressure,
    cigarettes per day, 
    body mass index, 
    heart rate, and
    glucose level
    Compute the following summary statistics 
    by age group:
    1. Count the number of subjects
    2. Mean
    3. Standard Deviation
    4. Minimum
    5. Median 
    6. Maximum
    
```{r q4, message=FALSE, warning=FALSE}



```

