---
title: "Homework # 1"
author: "YOUR NAME HERE"
date: "2026-09-17"
output: html_document
---


### Loading Package


```{r packages, message=FALSE, warning=FALSE}
library(tidyverse)

```


Note: To receive credit, codes must follow the structure discussed in class. 

### Exercise 3

Write the code to recreate the correct output on Exercise 3. 

```{r ex3, message=FALSE, warning=FALSE}




```


### Exercise 4

Write the code to recreate the correct output on Exercise 4. 

```{r ex4, message=FALSE, warning=FALSE}



```



### Exercise 5

Write the code to get the output for Exercise 5. 

```{r ex5, message=FALSE, warning=FALSE}




```


### Exercise 6

Write the code to recreate the ANOVA table on Exercise 6. 

```{r ex6, message=FALSE, warning=FALSE}





```


### Exercise 7

Write the code to recreate the ANOVA table on Exercise 7. 

```{r ex7, message=FALSE, warning=FALSE}





```


### Exercise 8

Write the code to recreate the ANOVA table on Exercise 8. 

```{r ex8, message=FALSE, warning=FALSE}





```


### Exercise 9

Write the code to get the ANOVA table on Exercise 9.

```{r ex9, message=FALSE, warning=FALSE}








```

### Exercise 10

Write the code to get the output for Exercise 10.

```{r ex10, message=FALSE, warning=FALSE}

 

```


### Exercise 11

Write the code to get the output for Exercise 11.



```{r ex11, message=FALSE, warning=FALSE}



```